quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-08-17 paper-quollr.Rmd
Initial work adding NLDR link plots

```{r, eval=knitr::is_latex_output(), fig.pos='H', fig.cap="$2\text{-}D$ projections of the lifted high-dimensional wireframe model from the `Scurve` UMAP layout. Each panel (a1–a4) shows the model (black) overlaid on `Scurve` data (in purple) in different projections. These views illustrate how the lifted wireframe model captures the structure of the `Scurve` data. The two twists visible in the UMAP layout can also be seen in the lifted model."}

@@

>>>>

```{r, eval=knitr::is_latex_output(), fig.pos='H', fig.cap="$2\\text{-}D$ projections of the lifted high-dimensional wireframe model from the `Scurve` UMAP layout. Each panel (a1–a4) shows the model (black) overlaid on `Scurve` data (in purple) in different projections. These views illustrate how the lifted wireframe model captures the structure of the `Scurve` data. The two twists visible in the UMAP layout can also be seen in the lifted model."}

@@

```{r}
## Create the first row of selection
scurve_umap_scaled_select1 <- scurve_umap_scaled |>
  mutate(select_area = if_else(emb1 <= 0.7 & emb1 >= 0.4 & emb2 <= 0.25 & emb2 >= 0, "selected", "deselected"))

scurve_umap_scaled_select1_selected <- scurve_umap_scaled_select1 |>
  filter(select_area == "selected")

scurve_umap_scaled_select1_deselected <- scurve_umap_scaled_select1 |>
  filter(select_area == "deselected")

scurve_umap_plt_select1 <- ggplot(
  scurve_umap_scaled_select1_deselected, 
  aes(x = emb1, y = emb2)) +
  geom_point(alpha = 0.5, color = clr_choice, size = 0.5) +
  geom_point(data = scurve_umap_scaled_select1_selected, aes(x = emb1, y = emb2), alpha = 0.5, color = "#756bb1", size = 0.5) +
  interior_annotation("a1") +
  xlim(sc_xlims) +
  ylim(sc_ylims)

## Create the second row of selection
scurve_umap_scaled_select2 <- scurve_umap_scaled |>
  mutate(select_area = if_else(emb1 <= 0.55 & emb1 >= 0.25 & emb2 <= 1.25 & emb2 >= 0.75, "selected", "deselected"))

scurve_umap_scaled_select2_selected <- scurve_umap_scaled_select2 |>
  filter(select_area == "selected")

scurve_umap_scaled_select2_deselected <- scurve_umap_scaled_select2 |>
  filter(select_area == "deselected")

scurve_umap_plt_select2 <- ggplot(
  scurve_umap_scaled_select2_deselected, 
  aes(x = emb1, y = emb2)) +
  geom_point(alpha = 0.5, color = clr_choice, size = 0.5) +
  geom_point(data = scurve_umap_scaled_select2_selected, aes(x = emb1, y = emb2), alpha = 0.5, color = "#756bb1", size = 0.5) +
  interior_annotation("b1") +
  xlim(sc_xlims) +
  ylim(sc_ylims)
```

```{r, eval=knitr::is_latex_output(), fig.pos='H'}
scurve_umap_plt_select1 + scurve_umap_plt_select1 +
  scurve_umap_plt_select2 + scurve_umap_plt_select1 +
  plot_layout(ncol = 2)
```

### 2025-08-17 paper-quollr.tex
Updated the limit
Initial work adding NLDR link plots

The generated p-D model, overlaid with the data, can also be visualized using \texttt{show\_langevitour}. Additionally, it features a function for visualizing the \(2\text{-}D\) projection of the fitted model overlaid on the data, called \texttt{plot\_proj}.

@@

\begin{figure}[H]
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-27-1} \caption{$2 ext{-}D$ projections of the lifted high-dimensional wireframe model from the `Scurve` UMAP layout. Each panel (a1–a4) shows the model (black) overlaid on `Scurve` data (in purple) in different projections. These views illustrate how the lifted wireframe model captures the structure of the `Scurve` data. The two twists visible in the UMAP layout can also be seen in the lifted model.}\label{fig:unnamed-chunk-27}
\end{figure}

@@

>>>>

The generated \(p\text{-}D\) model, overlaid with the data, can also be visualized using \texttt{show\_langevitour}. Additionally, it features a function for visualizing the \(2\text{-}D\) projection of the fitted model overlaid on the data, called \texttt{plot\_proj}.

@@

\begin{figure}[H]
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-27-1} \caption{$2\text{-}D$ projections of the lifted high-dimensional wireframe model from the `Scurve` UMAP layout. Each panel (a1–a4) shows the model (black) overlaid on `Scurve` data (in purple) in different projections. These views illustrate how the lifted wireframe model captures the structure of the `Scurve` data. The two twists visible in the UMAP layout can also be seen in the lifted model.}\label{fig:unnamed-chunk-27}
\end{figure}

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-30-1}
